{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-01 Paper/main.tex
Correction on 3.2

	The Hilbert space of square integrable functions on $[0,1]$ {\color{orange} (instead, $\mathbb{L}^2[0,1]$)} is the function space that is most often used for theoretical considerations in functional data analysis  {\color{orange} without loss of generality}.

>>>>

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality. We also focus on the interval [0,1] for the purpose of this paper.	The random function defined on $\mathbb{L}^2[0,1]$ can be represented as
